\section{Conclusion}
\label{sec:conclusion}

We introduced KG-SCoRE, a pipeline that uses query-time LLM-based KG verification to clean noisy triples, scaffold hypothesis generation with verified KG paths, and rerank hypotheses by faithfulness to their paths. Under fair evaluation, KG-SCoRE achieves the highest LLM-judged StrictFaith@10 (0.38, vs.\ ToG's 0.35 and RoG's 0.09) and BroadFaith@10 of 1.00. On the 20-pair multi-seed evaluation ($n{=}60$), KG-SCoRE matches RoG (Hit@10 0.40), while significantly outperforming ToG, Vanilla LLM, and BM25-RAG. On a small KGQA probe, KG-SCoRE achieves the best EM (0.30). A key ablation finding is that ComplEx-based learned scoring harms recall on noisy KGs (MRR=0.013), and a rule-based cleaning baseline (F1=0.038) confirms that LLM verification is necessary despite its imperfect precision. We report transparently that the reranking-driven StrictFaith gain is partly judge-dependent: under an independent rule-based judge, the gain largely does not transfer, underscoring the need for trained entailment models.

\paragraph{Limitations.}
(1) The 20-pair benchmark is small; faithfulness is measured on 10 pairs. (2) The synthetic KG uses type-violation noise, which differs from real SemMedDB errors (negation, entity-linking, context). (3) Faithfulness labels come from an LLM judge with low fine-grained reliability ($\kappa{\approx}0$); the StrictFaith reranking gain is partly circular (Table~\ref{tab:robust}), as the same judge drives reranking and scoring. (4) Classic Swanson pairs may be in the LLM's training data, inflating recall; a time-split evaluation is needed. (5) The KGQA probe is small (10 single-hop questions from the same KG) and does not establish broad generalization. (6) The system traces hypotheses to synthetic KG paths, not to literature evidence (PMIDs, source sentences). (7) No biomedical expert evaluation. (8) Statistical tests treat 3 seeds $\times$ 20 pairs as $n{=}60$; since per-seed variance is near zero, query-level paired tests would be more conservative.

\paragraph{Future work.}
(1) Scale to real SemMedDB with time-split LBD evaluation and literature-level provenance (PMIDs, evidence sentences). (2) Replace the LLM faithfulness judge with a trained entailment model, and evaluate StrictFaith gains under fully independent judges. (3) Add deterministic and learned KG-cleaning baselines, and evaluate correction accuracy. (4) Evaluate on standard KGQA benchmarks (WebQSP, MetaQA) with multi-hop questions. (5) Conduct blind biomedical expert evaluation. We release code and data to facilitate replication.
