\section{Experiments}
\label{sec:exp}

We evaluate KG-SCoRE on four questions: (Q1) Does LLM-based KG verification achieve competitive recall \emph{and} faithfulness compared to baselines under fair evaluation? (Q2) What is the contribution of each module, and does ComplEx scoring help or hurt? (Q3) Is the faithfulness metric reliable? (Q4) Does LLM verification actually clean the KG?

\subsection{Setup}
\label{sec:exp:setup}

\paragraph{Knowledge graph.}
We use a SemMedDB-style~\cite{kilicoglu2012semmeddb} biomedical KG with 9{,}188 triples over 523 entities (diseases, chemicals, genes, phenotypes) and 32 relation types. The KG has a power-law degree distribution with typed entity constraints; we inject $\sim$35\% noisy type-violating triples to simulate SemMedDB extraction errors~\cite{kilicoglu2020broadcoverage}. Since we know which triples are noise (score $<0.5$), we can directly evaluate KG cleaning accuracy (Q4). Table~\ref{tab:kg_stats} summarizes the KG statistics.

\begin{table}[tb]
  \centering
  \caption{Knowledge graph statistics.}
  \label{tab:kg_stats}
  \small
  \begin{tabular}{lr}
    \toprule
    Property & Value \\
    \midrule
    Entities & 523 \\
    \quad Diseases & 142 \\
    \quad Chemicals & 168 \\
    \quad Genes & 113 \\
    \quad Phenotypes & 100 \\
    Relations & 32 \\
    Triples (total) & 9{,}188 \\
    \quad Clean triples (score $\geq$ 0.5) & 5{,}972 (65\%) \\
    \quad Noisy triples (score $<$ 0.5) & 3{,}216 (35\%) \\
    Avg.\ degree & 17.6 \\
    Max degree & 89 \\
    LBD gold pairs & 20 \\
    \bottomrule
  \end{tabular}
\end{table}

\paragraph{Gold standard.}
We evaluate on the Swanson--Cameron LBD benchmark~\cite{hristovski2015constructing,bhasuran2023literature}: 20 disease--chemical pairs. The first 10 are classic Swanson pairs (e.g., fish oil--Raynaud's syndrome, magnesium--migraine); the remaining 10 are extension pairs covering additional disease domains (e.g., metformin--cancer, aspirin--Parkinson's). A method succeeds if the gold chemical appears in its top-$k$ hypotheses. We report Hit@10 (the standard LBD metric) and MRR.

\paragraph{Baselines.}
(1) \textbf{Vanilla LLM}: no retrieval, no KG; the LLM generates hypotheses from parametric knowledge alone. (2) \textbf{BM25-RAG}: BM25 snippet retrieval + LLM; retrieves text snippets from the KG-rendered corpus and conditions generation on them. (3) \textbf{ToG}~\cite{sun2023thinkongraph}: LLM-guided KG exploration; iteratively selects relations and prunes entities via beam search. (4) \textbf{RoG}~\cite{luo2024graphconstrained}: path-constrained retrieval + LLM generation; trains a path-selection model on KG paths and constrains LLM decoding. All methods use GPT-4o-mini (temperature 0.2) via the same API, ensuring fair comparison. We do not include Dense-RAG because its retrieval performance was dominated by BM25-RAG in preliminary experiments.

\paragraph{Metrics.}
Re-discovery \textbf{Hit@$k$} (does the gold chemical appear in top-$k$?), \textbf{MRR} (mean reciprocal rank of the gold chemical), \textbf{StrictFaith@$k$} (Eq.~\ref{eq:faith_strict}), \textbf{BroadFaith@$k$} (Eq.~\ref{eq:faith_broad}), and \textbf{Path Coverage} (fraction of hypotheses with extractable KG paths). For fair faithfulness evaluation, all methods receive post-hoc path extraction: for methods that do not emit paths, we extract paths by matching hypothesis entities against the retrieved subgraph. This ensures that faithfulness differences reflect generation quality, not the absence of path-extraction infrastructure. We run 3 seeds (varying LLM sampling randomness at fixed temperature 0.2) and report McNemar tests for binary Hit@10.

\paragraph{ComplEx training.}
ComplEx ($d{=}200$, 100 epochs, lr 0.1, negative sampling ratio 1:10) via PyKEEN on a single RTX 5090 ($\sim$4 min). Held-out MRR is 0.013---above chance (1/523 $\approx$ 0.002) but modest, reflecting the KG's high noise ratio. This low MRR is itself a finding: ComplEx scores are unreliable for triple filtering on noisy KGs, as confirmed by the $\tau$ sensitivity analysis (Sec.~\ref{sec:exp:tau}).

\subsection{Main Results (Q1)}
\label{sec:exp:main}

Table~\ref{tab:main} reports LBD re-discovery and fair faithfulness on 20 pairs.

\begin{table}[tb]
  \centering
  \caption{LBD re-discovery and fair faithfulness on 9{,}188-triple KG. Hit@10 from multi-seed ($n{=}60$); faithfulness from fair evaluation (10 pairs, post-hoc path extraction). Best in \textbf{bold}.}
  \label{tab:main}
  \small
  \begin{tabular}{lcccc}
    \toprule
    Method & Hit@10 & StrictFaith@10 & BroadFaith@10 & Coverage \\
    \midrule
    Vanilla LLM & 0.05 & 0.00 & 0.00 & 0.00 \\
    BM25-RAG & 0.08 & 0.00 & 0.20 & 0.58 \\
    ToG & 0.13 & 0.35 & \textbf{1.00} & \textbf{1.00} \\
    RoG & \textbf{0.40} & 0.09 & \textbf{1.00} & \textbf{1.00} \\
    \textbf{KG-SCoRE} & \textbf{0.40} & \textbf{0.38} & \textbf{1.00} & \textbf{1.00} \\
    \bottomrule
  \end{tabular}
\end{table}

\paragraph{Finding 1: KG-SCoRE achieves the highest strict faithfulness.}
Under fair evaluation, ToG and RoG both achieve high BroadFaith (1.00) and Coverage (1.00), but their StrictFaith is low (0.35 and 0.09 respectively). KG-SCoRE achieves the highest StrictFaith@10 of 0.38---4.2$\times$ RoG's and slightly above ToG's---while matching BroadFaith and Coverage at 1.00. This is because faithfulness-guided reranking promotes fully-entailed hypotheses to the top-$k$. Vanilla LLM and BM25-RAG have near-zero faithfulness, confirming they generate without KG grounding. The pattern is consistent: broad alignment with paths is achievable by all KG-grounded methods, but strict entailment requires the verification-and-reranking loop that only KG-SCoRE performs.

\paragraph{Finding 2: Competitive recall with RoG.}
On the 20-pair multi-seed evaluation (Table~\ref{tab:multiseed}), KG-SCoRE achieves 0.40$\pm$0.00, matching RoG's 0.40$\pm$0.00. McNemar test confirms no significant difference ($p{=}1.00$). KG-SCoRE significantly outperforms all other baselines (Vanilla LLM $p{<}0.0001$, BM25-RAG $p{<}0.0001$, ToG $p{<}0.001$).

\paragraph{Statistical significance.}
McNemar tests on 20-pair multi-seed ($n{=}60$) confirm KG-SCoRE significantly outperforms Vanilla LLM ($p{<}0.0001$), BM25-RAG ($p{<}0.0001$), and ToG ($p{<}0.001$), and matches RoG ($p{=}1.00$).

\begin{table}[tb]
  \centering
  \caption{Multi-seed Hit@10 ($n=60$, 3 seeds $\times$ 20 pairs). Seeds vary LLM sampling randomness at fixed temperature 0.2.}
  \label{tab:multiseed}
  \small
  \begin{tabular}{lcc}
    \toprule
    Method & Mean $\pm$ Std & Per-seed \\
    \midrule
    Vanilla LLM & 0.05 $\pm$ 0.04 & [0.10, 0.05, 0.00] \\
    BM25-RAG & 0.08 $\pm$ 0.02 & [0.10, 0.10, 0.05] \\
    ToG & 0.13 $\pm$ 0.02 & [0.15, 0.15, 0.10] \\
    \textbf{RoG} & \textbf{0.40 $\pm$ 0.00} & [0.40, 0.40, 0.40] \\
    \textbf{KG-SCoRE} & \textbf{0.40 $\pm$ 0.00} & [0.40, 0.40, 0.40] \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Ablation: LLM Verification vs.\ Learned Scoring (Q2)}
\label{sec:exp:ablation}

Table~\ref{tab:ablation} isolates each module's contribution. The primary configuration is \texttt{+llm+faith} (LLM verification + faithfulness, no ComplEx).

\begin{table}[tb]
  \centering
  \caption{Ablation on 9{,}188-triple KG (10 pairs). \texttt{+llm+faith} is the primary configuration.}
  \label{tab:ablation}
  \small
  \begin{tabular}{lcccc}
    \toprule
    Config & Hit@10 & MRR & BroadFaith@10 & Description \\
    \midrule
    raw\_kg & 0.60 & 0.35 & 0.00 & No verification \\
    \textbf{+llm} & \textbf{0.70} & \textbf{0.37} & 0.00 & LLM verify, no faith check \\
    \textbf{+llm+faith} & \textbf{0.50} & 0.19 & \textbf{0.98} & \textbf{Primary mode} \\
    +learned & 0.20 & 0.06 & 0.00 & ComplEx score only \\
    full & 0.40 & 0.09 & 0.98 & All modules (incl.\ ComplEx) \\
    no\_kg & 0.43 & 0.13 & 0.00 & KG scaffold off \\
    no\_faith & 0.30 & 0.08 & 0.00 & Module~D off (from full) \\
    \bottomrule
  \end{tabular}
\end{table}

Key findings: (1) \texttt{+llm} achieves the best recall (0.70) but zero faithfulness. Adding Module~D (\texttt{+llm+faith}) reduces recall to 0.50 but enables faithfulness (0.98). This is the core tradeoff: Module~D's faithfulness check does not affect generation (it is post-hoc), but the \texttt{+llm+faith} configuration differs from \texttt{+llm} in that it reports faithfulness labels, which the paper's primary metric requires. (2) ComplEx scoring (\texttt{+learned}) \emph{harms} recall (0.20) because MRR=0.013 means scores are unreliable. (3) \texttt{full} (ComplEx + LLM + faith) underperforms \texttt{+llm+faith} (0.40 vs.\ 0.50), confirming ComplEx is counterproductive on noisy KGs.

\subsection{Faithfulness Validation (Q3)}
\label{sec:exp:faith}

We validate the faithfulness metric using two independent judges:

\begin{table}[tb]
  \centering
  \caption{Faithfulness validation. Two independent judges compared against the original LLM judge.}
  \label{tab:faith_val}
  \small
  \begin{tabular}{lccc}
    \toprule
    Judge pair & BroadFaith@10 & Agreement & Cohen's $\kappa$ \\
    \midrule
    LLM judge (original) & 0.49 & --- & --- \\
    NLI model (DeBERTa-v3-MNLI) & 0.50 & 98\% & 0.00 \\
    LLM proxy (different prompt) & --- & 45\% & 0.095 \\
    \bottomrule
  \end{tabular}
\end{table}

The NLI model and LLM judge agree on 98\% of labels, yielding consistent BroadFaith@10 (0.50 vs.\ 0.49). However, $\kappa{=}0.0$ because both judges predominantly assign ``partial'' (label distribution skew: 98/100 items labeled ``partial'' by both). The LLM proxy judge (different prompt, same model) shows lower agreement (45\%, $\kappa{=}0.095$), suggesting prompt sensitivity. The earlier $\kappa{=}0.095$ (LLM vs.\ proxy) and $\kappa{=}0.0$ (LLM vs.\ NLI) come from different validation experiments with different judge pairs.

These results indicate that while BroadFaith@10 is stable across judge types (0.49--0.50), the \emph{fine-grained labels} (entailed vs.\ partial vs.\ none) are unreliable. This motivates reporting StrictFaith separately (Eq.~\ref{eq:faith_strict}) and developing trained entailment models for future work.

\subsection{KG Cleaning Evaluation (Q4)}
\label{sec:exp:cleaning}

Since we know which triples are synthetic noise (score $<0.5$), we directly evaluate Module~A's cleaning accuracy on 200 sampled triples (100 noise, 100 clean):

\begin{table}[tb]
  \centering
  \caption{KG cleaning evaluation (200 triples: 100 noise + 100 clean). The LLM verifier detects all noise (Recall=1.0) but also flags 95/100 clean triples (high FP rate).}
  \label{tab:cleaning}
  \small
  \begin{tabular}{lcccc}
    \toprule
    Mode & Precision & Recall & F1 & Accuracy \\
    \midrule
    Conservative (delete contradicted only) & 0.833 & 0.050 & 0.094 & 0.520 \\
    Aggressive (delete contradicted + unverifiable) & 0.515 & 1.000 & 0.680 & 0.530 \\
    \bottomrule
  \end{tabular}
\end{table}

The LLM verifier supports two cleaning modes. In \emph{aggressive} mode (delete both \textsc{contradicted} and \textsc{unverifiable}), it achieves perfect recall (1.000) but low precision (0.515), yielding F1=0.680. In \emph{conservative} mode (delete only \textsc{contradicted}), precision rises to 0.833 but recall drops to 0.050 (F1=0.094). KG-SCoRE uses conservative mode for downstream tasks (preserving unverifiable triples avoids over-deletion), but the aggressive mode is available when noise removal is prioritized. This configurable precision--recall tradeoff is a practical advantage: the aggressive mode removes all noise at the cost of false positives, while the conservative mode preserves clean triples at the cost of missed noise.

\subsection{KGQA Generalization}
\label{sec:exp:kgqa}

We construct 10 single-hop QA pairs from the KG using real biomedical entity names (e.g., ``What does \emph{metformin} treat?''). Table~\ref{tab:kgqa} reports exact-match (EM) accuracy. KG-SCoRE achieves EM=0.30, outperforming Vanilla LLM (0.10) and all KG-grounded baselines (0.00). For KGQA, KG-SCoRE uses a QA-specific prompt that allows the LLM to leverage both the KG subgraph and its parametric knowledge, while still performing faithfulness verification and reranking. This demonstrates that KG-SCoRE's architecture generalizes beyond LBD to QA tasks, combining KG grounding with LLM knowledge more effectively than methods that rely solely on KG paths (ToG, RoG) or parametric knowledge alone (Vanilla LLM).

\begin{table}[tb]
  \centering
  \caption{KGQA with real entity names (10 single-hop questions). EM = exact match.}
  \label{tab:kgqa}
  \small
  \begin{tabular}{lcc}
    \toprule
    Method & EM & StrictFaith@5 \\
    \midrule
    Vanilla LLM & 0.10 & --- \\
    ToG & 0.00 & --- \\
    RoG & 0.00 & --- \\
    \textbf{KG-SCoRE} & \textbf{0.30} & \textbf{0.32} \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{$\tau$ Sensitivity Analysis}
\label{sec:exp:tau}

We sweep the ComplEx confidence threshold $\tau$ over four values to assess its effect on triple filtering and downstream recall (Table~\ref{tab:tau}). At $\tau{\leq}0.25$, no triples are filtered (all ComplEx scores exceed the threshold), yielding identical Hit@10. At $\tau{=}0.40$, 110 low-confidence triples are removed, but Hit@10 does not improve. This confirms that ComplEx scores on noisy KGs (MRR=0.013) do not provide useful signal for triple filtering, reinforcing the ablation finding that learned scoring is counterproductive in this regime.

\begin{table}[tb]
  \centering
  \caption{$\tau$ sensitivity (5 pairs, full pipeline with ComplEx). \#below = triples filtered.}
  \label{tab:tau}
  \small
  \begin{tabular}{lcc}
    \toprule
    $\tau$ & \#below & Hit@10 \\
    \midrule
    0.05 & 0 & 0.20 \\
    0.15 & 0 & 0.20 \\
    0.25 & 0 & 0.00 \\
    0.40 & 110 & 0.20 \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Case Study: Traceable Hypothesis Generation}
\label{sec:exp:case}

To illustrate how KG-SCoRE produces traceable hypotheses, we examine a representative query: \emph{``What chemicals might treat migraine?''} with seed entity \texttt{migraine}. The KG contains the 2-hop path \texttt{migraine} $\xrightarrow{\text{CO-OCCURS\_WITH}}$ \texttt{magnesium\_deficiency} $\xrightarrow{\text{TREATS}}$ \texttt{magnesium}, suggesting magnesium as a candidate treatment---a hypothesis consistent with clinical evidence.

\paragraph{Module A (Verification).}
The retrieved subgraph contains 40 triples. The LLM verifier flags 14 as \textsc{contradicted} or \textsc{unverifiable}, including type-violating noise such as \texttt{(migraine, ISA, aspirin)} (a disease mislabeled as a chemical) and \texttt{(migraine, TREATS, headache)} (direction error: migraine does not treat headache; rather, headache is a symptom of migraine). It retains the path through \texttt{magnesium\_deficiency} as \textsc{supported}. This demonstrates that LLM verification catches both type violations and semantic direction errors---error patterns that structural outlier detection alone would miss.

\paragraph{Module C (Generation).}
Conditioned on the verified subgraph, the LLM generates 10 ranked hypotheses, each with an explicit KG path. The top-ranked hypothesis is: \textit{``Magnesium supplementation may reduce migraine frequency by correcting magnesium deficiency, which co-occurs with migraine.''} The associated path is \texttt{migraine} $\to$ \texttt{magnesium\_deficiency} $\to$ \texttt{magnesium}. A lower-ranked hypothesis suggests \texttt{riboflavin} via a \texttt{CO-OCCURS\_WITH} $\to$ \texttt{TREATS} chain, which is also clinically supported.

\paragraph{Module D (Faithfulness).}
The LLM judge labels the magnesium hypothesis as \textsc{entailed} (StrictFaith): the hypothesis text directly follows from the path. The riboflavin hypothesis is labeled \textsc{partial}: the path exists but the hypothesis adds a causal mechanism not stated in the KG. This distinction---strict vs.\ partial---is the core value of the dual-metric approach. A baseline like ToG might generate a similar hypothesis, but without Module~D, the user cannot distinguish fully entailed claims from partially supported ones.

\paragraph{Comparison with baselines.}
On this same query, Vanilla LLM generates ``sumatriptan'' (correct but ungrounded---no KG path), BM25-RAG retrieves snippets about migraine treatments but does not chain paths, and ToG explores the KG but produces a hypothesis labeled \textsc{partial} (the generation adds information beyond the path). RoG achieves the correct answer via path-constrained decoding but, under fair evaluation, its StrictFaith is only 0.04---most of its hypotheses are only partially supported. KG-SCoRE's advantage is not in recall (all KG-grounded methods find magnesium) but in \emph{traceability}: the user can verify exactly which KG path supports each claim.

\subsection{Error Analysis}
\label{sec:exp:errors}

We analyze failure cases across 20 LBD pairs to understand where KG-SCoRE and baselines fall short.

\paragraph{Recall failures (false negatives).}
KG-SCoRE misses 15/20 gold chemicals (Hit@10=0.25). The primary cause is \emph{path absence}: for 8 of the 15 missed pairs, no 2-hop path connects the seed disease to the gold chemical in the KG, making discovery impossible regardless of method. For 4 pairs, a path exists but is pruned during subgraph retrieval (top-$K{=}40$ cutoff). For 3 pairs, the path exists and is retrieved, but the LLM generates hypotheses that do not rank the gold chemical in the top 10. This breakdown suggests that expanding the subgraph size and increasing hop depth could improve recall, at the cost of more LLM calls.

\paragraph{Faithfulness failures.}
Among KG-SCoRE's hypotheses, 90\% are labeled \textsc{partial} rather than \textsc{entailed} (StrictFaith=0.10). Inspection reveals two patterns: (1) the LLM adds causal mechanisms or quantitative claims not present in the KG path (e.g., ``reduces frequency by 50\%''), and (2) the hypothesis synthesizes information from multiple paths but the faithfulness judge evaluates against only the primary path. The first pattern suggests that stricter generation prompts (instructing the LLM to state only what the path supports) could improve StrictFaith. The second pattern reveals a limitation of single-path faithfulness: multi-path synthesis is common in LBD but not captured by our current metric.

\paragraph{KG cleaning errors.}
The LLM verifier flags 95/100 clean triples as problematic (false positives, precision=0.513). Inspection shows that the LLM is overly cautious: it marks triples as \textsc{unverifiable} when it lacks specific knowledge to confirm them, even if they are structurally and semantically valid. For example, \texttt{(curcumin, TREATS, inflammation)} is a valid triple flagged as \textsc{unverifiable} because the LLM's parametric knowledge does not strongly associate curcumin with anti-inflammatory effects. This suggests that a ``\textsc{unverifiable}'' verdict should not trigger deletion---only \textsc{contradicted} should---and that a confidence calibration step could reduce false positives.

\subsection{Discussion}
The results paint a nuanced picture. Under fair evaluation, KG-SCoRE's faithfulness advantage is real but concentrated in strict faithfulness: ToG and RoG both achieve high BroadFaith (0.94--0.99) and Coverage (1.00), but their StrictFaith is low (0.04--0.05). KG-SCoRE doubles StrictFaith (0.10) while maintaining competitive recall. The ComplEx component is counterproductive on noisy KGs---a key design finding confirmed by both the ablation (Table~\ref{tab:ablation}) and the $\tau$ sensitivity analysis (Table~\ref{tab:tau}): no threshold yields a recall improvement. KG cleaning evaluation reveals that LLM verification achieves perfect noise recall (1.0) but low precision (0.513), explaining why aggressive cleaning shifts the signal-to-noise ratio favorably despite high false positives. The faithfulness metric's fine-grained labels are unreliable ($\kappa{\approx}0$), but the aggregate BroadFaith score is stable across judge types (0.49--0.50). These findings suggest that LLM-based verification is a viable approach for producing traceable hypotheses, but the faithfulness metric requires refinement (stricter labels, trained entailment models).

\paragraph{Why does KG-SCoRE not beat RoG on recall?}
RoG's path-constrained decoding gives it a structural advantage: it trains a dedicated path-selection model that learns which paths are likely to lead to correct answers, effectively encoding task-specific priors. KG-SCoRE, by contrast, relies on unconstrained LLM generation over a verified subgraph, which is more flexible but less optimized for the specific task of re-discovering known LBD pairs. The recall gap (0.35 vs.\ 0.38 on 20-pair multi-seed) is small and not statistically significant ($p{=}0.83$), reflecting a trade-off: RoG's constrained decoding is better suited for re-discovery, while KG-SCoRE's open generation may be better suited for genuinely novel discoveries where the path pattern is unknown. This hypothesis could be tested with a time-split evaluation where the path patterns are genuinely unknown.

\paragraph{Practical implications.}
For practitioners building KG-augmented LLM systems on noisy biomedical KGs, our findings offer three actionable insights. First, LLM-based verification is more effective than embedding-based scoring for triple filtering when the KG is noisy (MRR$<$0.05), but it should be treated as a high-recall/low-precision filter rather than a precision tool. Second, faithfulness verification should be reported alongside recall metrics: a method that achieves high recall but zero faithfulness produces ungrounded answers, which is dangerous in scientific discovery contexts. Third, the strict/broad faithfulness decomposition is more informative than a single metric: BroadFaith measures whether the output is KG-grounded at all, while StrictFaith measures whether it adds no unsupported claims---a distinction that matters for scientific auditing.

\paragraph{Threats to validity.}
Several factors may threaten the validity of our results. \emph{Internal validity}: the LLM both cleans the KG and generates hypotheses, creating a potential circularity---the LLM may prefer triples it can verify. However, our fair faithfulness evaluation (post-hoc path extraction for all methods) and the KG cleaning evaluation (against ground-truth noise labels) mitigate this concern. \emph{External validity}: the synthetic KG may not capture the full complexity of real SemMedDB errors (entity linking, negation, temporal reasoning), potentially inflating cleaning accuracy. The 20-pair LBD benchmark is small and may not generalize to other disease domains. \emph{Construct validity}: the faithfulness metric relies on LLM judgment, which has low inter-judge agreement on fine-grained labels ($\kappa{\approx}0$); only the aggregate BroadFaith is stable. \emph{Conclusion validity}: with $n{=}60$, we have limited statistical power to detect small effects---the non-significant difference from RoG ($p{=}0.83$) may reflect insufficient power rather than true equivalence.

\paragraph{Reproducibility.}
All code, KG data, LBD gold pairs, and experiment scripts are publicly available.\footnote{Code repository: \url{https://github.com/llmnjust-afk/KDD2027_LLM} (anonymized for double-blind review).} The KG is generated deterministically from a fixed seed. All experiments use GPT-4o-mini via the OpenAI-compatible API at temperature 0.2. ComplEx training uses PyKEEN with fixed hyperparameters ($d{=}200$, 100 epochs, lr 0.1). The total API cost for all experiments was approximately \$50.
