\section{Related Work}
\label{sec:related}

We situate KG-SCoRE at the intersection of four research threads: KG-augmented LLM reasoning, literature-based discovery, knowledge graph completion, and faithfulness evaluation in retrieval-augmented generation.

\paragraph{KG-augmented LLM reasoning.}
The integration of knowledge graphs with LLMs has matured into a rich research area~\cite{pan2023unifying,han2024graphrag}. Think-on-Graph (ToG)~\cite{sun2023thinkongraph} pioneered LLM-guided interactive exploration of KG neighborhoods, iteratively selecting relations and pruning entities through beam search; ToG~2.0~\cite{ma2024thinkongraph} added knowledge-guided retrieval with a domain-agnostic score function. Graph-constrained Reasoning (RoG)~\cite{luo2024graphconstrained} takes a complementary approach: it trains a path-selection model on KG paths and uses it to constrain LLM decoding, ensuring that generated reasoning chains follow valid KG trajectories. GNN-RAG~\cite{mavromatis2025gnnrag} uses graph neural networks to retrieve reasoning paths before feeding them to the LLM, combining structural reasoning with generative flexibility. Paths-over-Graph~\cite{tan2025pathsovergraph} further refines path search strategies with LLM-guided pruning, and StructGPT~\cite{jiang2023structgpt} iteratively queries structured data via specialized interfaces. A common limitation across these methods is that they treat the KG as an immutable, trusted resource: they do not \emph{refine} the KG, nor do they post-hoc verify whether the final output is entailed by a specific path. Recent work on grounding LLM reasoning under incomplete graph evidence~\cite{li2026grounding} and traceability in medical LLM reasoning~\cite{zhu2026hybrid} addresses related concerns but does not combine KG cleaning with post-hoc faithfulness verification. KG-SCoRE differs by closing a verification loop---the LLM both cleans the KG and verifies the output---and by reporting faithfulness@$k$ as a first-class metric.

\paragraph{Literature-based discovery and hypothesis generation.}
Literature-based discovery (LBD), introduced by Swanson's pioneering work on fish oil and Raynaud's syndrome~\cite{swanson1986undiscovered}, seeks hidden cross-disciplinary links by chaining literatures~\cite{hristovski2015constructing,bhasuran2023literature}. Classical LBD relies on co-occurrence statistics and graph traversal over SemMedDB~\cite{kilicoglu2012semmeddb,kilicoglu2020broadcoverage}, producing ranked candidate lists rather than explanatory hypotheses. Bitola and Arrowsmith exemplify this paradigm, using association measures over medical subject headings. The LLM era has revitalized LBD: Qi et al.~\cite{qi2024large} systematically evaluated LLMs as biomedical hypothesis generators across multiple disease domains, finding that LLMs can surface plausible but often ungrounded connections. Liu et al.~\cite{liu2024literature} combined literature and data signals for hypothesis generation, and BioVerge~\cite{yang2025bioverge} benchmarked self-evaluating agents that assess their own hypotheses. Tyagin et al.~\cite{tyagin2025biomedical} introduced graph-based context retrieval for explainability, showing that structured retrieval improves hypothesis quality. BioHarness~\cite{xiao2026bioharness} assembles evidence across literature, knowledge bases, and atlases for multi-modal biomedical reasoning. These works focus on retrieval and generation quality but do not co-refine the underlying KG or quantitatively measure faithfulness against symbolic paths. KG-SCoRE unifies LBD's symbolic graph heritage with LLM generation under a single auditable loop, bridging the gap between classical graph-based LBD and modern LLM-driven discovery.

\paragraph{Knowledge graph embedding and completion.}
KG-completion models learn low-dimensional embeddings to score triple plausibility and predict missing links~\cite{ji2021survey,hogan2021knowledge,rossi2021knowledge}. TransE~\cite{bordes2013irreflexive} models relations as translations in embedding space, suitable for one-to-one relations. ComplEx~\cite{trouillon2016complex,trouillon2017knowledge} extends this to complex-valued embeddings, capturing antisymmetric and asymmetric relation patterns. ConvE~\cite{dettmers2018convolutional} applies 2D convolutions over reshaped embeddings for richer feature interactions, and R-GCN~\cite{schlichtkrull2018modeling} uses graph convolutions with relation-specific weight matrices. RotatE~\cite{sun2019rotate} models relations as rotations in complex space, capturing composition patterns. We adopt ComplEx for its efficiency and expressiveness, but repurpose its scores not for link prediction alone---rather, to \emph{gate} LLM verification of suspect triples. However, our experiments reveal a critical finding: when the KG is noisy (MRR$<$0.05), ComplEx scores are unreliable for triple filtering and can actively harm downstream recall. This negative result has practical implications for KG-augmented LLM systems that assume embedding quality.

\paragraph{KG noise detection and quality assessment.}
Beyond embedding-based approaches, several works address KG noise directly. Paulheim and Bizer used statistical outlier detection to identify suspect triples in DBpedia, while subsequent work trained classifiers on graph features to flag incorrect facts~\cite{yao2021typing}. In the biomedical domain, SemRep's own precision has been extensively studied~\cite{kilicoglu2020broadcoverage}, with error analysis revealing systematic issues in negation handling, direction errors, and entity linking. Recent LLM-based approaches use language models to verify factual claims~\cite{min2023factscore} or detect hallucinated content~\cite{zhao2026survey}. KG-SCoRE applies LLM verification specifically to KG triples within a reasoning pipeline, measuring cleaning accuracy directly against known noise labels---an evaluation absent from prior KG-augmented LLM work.

\paragraph{RAG, faithfulness, and grounding.}
Retrieval-augmented generation grounds LLM outputs in retrieved passages~\cite{brown2025systematic,neha2025retrievalaugmented}. Faithfulness in RAG is typically measured via entailment between the output and retrieved text, using NLI models or question-generation--answering approaches~\cite{honovich2021evaluating}, or LLM-based judges~\cite{min2023factscore}. GraphRAG~\cite{han2024graphrag} constructs a KG from text and uses community-level summarization for retrieval. However, RAG faithfulness is measured against retrieved \emph{text}, not against explicit \emph{symbolic paths}. Our faithfulness@$k$ metric verifies entailment against KG paths, providing a stronger, structured grounding guarantee than passage-level overlap. The decomposition into strict and broad variants addresses the concern that ``partial'' support may overstate grounding---a nuance absent from standard RAG faithfulness metrics.
